\documentclass[11pt,a4paper]{article}
\usepackage{amsmath,amsfonts,bm}
\usepackage{caption,booktabs}
\usepackage{tabularx}
\usepackage{siunitx}
%\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{bibentry}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{MnSymbol}
\usepackage{mathtools}
%\usepackage[numbers]{natbib}
\usepackage[round]{natbib}
\usepackage[compact]{titlesec}
\usepackage[acronym]{glossaries} % Used to make a list of abbreviations
\usepackage{afterpage}
\usepackage[export]{adjustbox}[2011/08/13]
\usepackage{float}
\usepackage{multirow}
\usepackage{dcolumn}
\usepackage{lineno}
\usepackage{seqsplit}
\usepackage{hyperref}	
\usepackage{afterpage}
\usepackage{float}
\usepackage[top=3.0cm, bottom=2.25cm, left=3.5cm, right=3.0cm, headheight=16.5pt, includeheadfoot]{geometry}
\usepackage[parfill]{parskip}

\DeclareSIUnit \h {$h$}
\DeclareSIUnit \parsec {pc}
\newcommand{\boxsize}{$300^{\prime} \times 300^{\prime}$}
\newcommand{\smallboxsize}{$10^{\prime} \times 10^{\prime}$}
\newcommand{\mediumboxsize}{$50^{\prime} \times 50^{\prime}$}
\newcommand{\pending}[1]{\textcolor{red}{#1}}
\newcommand{\arcmin}{\ensuremath{^{\prime}}}
\newcommand{\figwidth}{1.0\textwidth}
\newcommand{\bL}{\bm{\ell}}
\newcommand{\kappaonehalofull}{$\kappa^{1h}(\theta)$}
\newcommand{\kappatwohalofull}{$\kappa^{2h}(\theta)$}
\newcommand{\kappatotalmz}{${\kappa}(M, z)$}
\newcommand{\kappatotalaalphaz}{${\kappa}^{tot}(A, \alpha, z)$}
\newcommand{\kappaonehalo}{${\kappa}^{1h}$}
\newcommand{\kappatwohalo}{${\kappa}^{2h}$}
\newcommand{\kappatotal}{${\kappa}^{tot}$}
\newcommand{\kappaonehalomz}{${\kappa}^{1h}(M,z)$}
\newcommand{\kappatwohalomz}{${\kappa}^{2h}(M, z)$}

\begin{document}
\begin{center}
Examiner report
\end{center}
I thank the Examiner for the thorough read and useful comments on my thesis. My response to Examiner's questions are
in blue.


**** Chapter 1 ****

page 2 Eq (1.4) units {$\rm$ yr} instead of yr

p. 3 Use $\Omega_\Lambda$ (capital Lambda) instead of $\Omega_\lambda$ to be consistent with the notations in the rest of the manuscript.

p. 10 Eq. (1.30)  it should be $a^X_lm$ and not $a^T_lm$

p. 10 link to Fig. 1.4 not valid is show in Fig. ?? 

p. 14 typo Type Ia supernovaes are the excellent standard candles -> Type Ia supernovae are excellent standard candles
theromonu- clear explosion -> thermonuclear explosion
The best measurement BAO scale comefrom CMB -> comes from
Use $H_o$ instead of $H_O$ to have notations consistent across the manuscript.

\textcolor{blue}{I thank referee for pointing out the mistakes and I have corrected it accordingly in the updated manuscript.}


**** Chapter 2 ****

p. 16 I don?t understand how Eq. (2.12) is derived from Eq. (2.11). I think that Eq. (2.12) should be removed from the manuscript.

\textcolor{blue}{removed}

p. 16 Eq. (2.14) Use $\ln$ for logarithm

p. 18 and 19 Use $erfc$ $\exp$ $\ln$ for these functions in math mode

p. 19 in a sphere of radius 8Mpc  to be replaced by in a sphere of radius $8 h^{-1} \, {\rm Mpc}$.

\textcolor{blue}{all the above corrections have be incorporated in the updated thesis.}

**** Chapter 3 ****

p. 33 Use kappa instead of k in the paragraph between Eq. (3.4) and Eq. (3.5).

p. 47 Caption of Fig. 3.4 Remove space between b and l in b lack triangles 

p. 53 Table 3.2 please specify the cluster mass and redshift in the caption. Cluster mass 2 × 1014M? and redshift z = 0.7. 

\textcolor{blue}{Changes have been made to the updated thesis as per referees comments.}

**** Chapter 4 ****

p. 65 we have niether included -> neither
\\\textcolor{blue}{corrected}

**** Chapter 6 ****

p. 102 last word astophysical to be corrected in astrophysical
\\\textcolor{blue}{corrected}


\end{document}